Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-18 paper/ijcai/paper.tex
fixed some citations

Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk \Fix{cite} test is performed to test for normality in the three techniques. With 99 \% of confidence, the results tell us that the distributions are not normal. Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman \Fix{cite}. The null-hypothesis is that all distributions are the same. With 99 \% of confidence, the results show that the distributions are not all the same. In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis \Fix{cite}. Figure \ref{fig:performance} report the results of that analysis for all the distributions. With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.

>>>>

Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10). With 99 \% of confidence, the results tell us that the distributions are not normal. Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman ~\cite{10.2307/2279372}. The null-hypothesis is that all distributions are the same. With 99 \% of confidence, the results show that the distributions are not all the same. In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis \Fix{cite}. Figure \ref{fig:performance} report the results of that analysis for all the distributions. With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.
